SunPy - Python for Solar Physics

### 2014-01-20 2-2-Lightcurve.tex

\subsection{Lightcurve}

@@

A \textit{Lightcurve} object may be created using a range of different methods. Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see example below). In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object.

\begin{lstlisting}[language=Python]
from sunpy import lightcurve
goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
`2011-06-07 08:00')
goes.peek()

@@

Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see example below).

\begin{lstlisting}[language=Python]
from sunpy import lightcurve
file=`lyra_20110607-000000_lev2_std.fits'
lyra=lightcurve.LYRALightCurve.create(file)
lyra.peek()

@@

>>>>

\subsection{Lightcurve}
\lstset{frame=single}

@@

\subsubsection{Creating and using Lightcurves}

A \textit{Lightcurve} object may be created using a range of different methods. Firstly, a \textit{Lightcurve} may be created for a specific instrument based on an input time range (see Listing \ref{goes_lc_code} below). In this example, the Lightcurve constructor searches remote sites for the GOES X-ray data specified by the time interval, downloads the required files and subsequently creates the object (see also Figure \ref{goes_lc}).

\begin{lstlisting}[language=Python,caption = Creating a GOES lightcurve using a time range.,label=goes_lc_code]
>>> from sunpy import lightcurve
>>> goes=lightcurve.GOESLightCurve.create(`2011-06-07 06:00',
`2011-06-07 08:00')
>>> goes.peek()

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{goes_lightcurve.pdf}
\caption{GOES lightcurve for the time interval 06:00 - 08:00 UT on 2011 June 7, plotted with the default parameters using the peek command (see Listing 1).}
\label{goes_lc}
\end{center}
\end{figure}

Alternatively, if the data file already exists on the local system, the \textit{Lightcurve} object may instead be initialized using that file as input (see Listing \ref{lyra_lc_code} below and Figure \ref{lyra_lc}).

\begin{lstlisting}[language=Python, caption = Creating a LYRA lightcurve using an existing data file.,label=lyra_lc_code]
>>> from sunpy import lightcurve
>>> file=`lyra_20110607-000000_lev2_std.fits'
>>> lyra=lightcurve.LYRALightCurve.create(file)
>>> lyra.peek()

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{lyra_lightcurve.pdf}
\caption{LYRA lightcurve for the full day of 2011 June 7, plotted with the default parameters using the peek command (see Listing 2).}
\label{lyra_lc}
\end{center}
\end{figure}

Once the \textit{Lightcurve} has been created it may be manipulated in a variety of ways in order to perform time series analysis. Continuing from the above, we show a few simple examples of using a LYRA lightcurve.

In the above case (Listing \ref{lyra_lc_code}), we created a LYRA Lightcurve spanning the full day of 2011 June 7. To extract the sub-interval 06:00 - 07:00 UT into a new \textit{Lightcurve} called \verb|lyra_zoom| we simply do the following:

\begin{lstlisting}[language=Python, ,caption = Extracting a sub-interval from a Lightcurve., label=lyra_truncate]
>>> from sunpy.time import TimeRange
>>> tran=TimeRange('2011-06-07 06:00','2011-06-07 07:00')
>>> lyra_zoom = lyra.truncate(tran)

Also in the example shown in Listing \ref{lyra_lc_code}, direct access to the data and time information in the object is available through \verb|lyra.data| and \verb|lyra.data.index| respectively.

\begin{lstlisting}[language=Python, caption = Accessing the data and time axis in a Lightcurve]
>>> print lyra.data
<class 'pandas.core.frame.DataFrame'>
DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
2011-01-28 23:59:59.983993
Data columns (total 4 columns):
CHANNEL1    1496629  non-null values
CHANNEL2    1496629  non-null values
CHANNEL3    1496629  non-null values
CHANNEL4    1496629  non-null values
dtypes: float64(4)

>>> print lyra.data.index
<class 'pandas.tseries.index.DatetimeIndex'>
[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
Length: 1496629, Freq: None, Timezone: None
\end{lstlisting}
